% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zhihao Wang}

\basicInfo{\centering{
  \email{nocap.wzh@gmail.com} \textperiodcentered\ 
  \phone{(+86) 176-965-96969} \textperiodcentered\ 
  \faMale \ Age 20 
}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Harbin Institute of Technology (Weihai)}, Shandong, China}{2020 -- Present}
\begin{itemize}[parsep=0.5ex]
  \item \textit{B.S.} in Intelligent Vehicle Engineering , expected June 2024
  \item GPA:\textbf{92.36}/100\quad
  Rank:\textbf{3}/73\quad 
  Top:\textbf{4.1\%}\quad
  TOEFL:\textbf{99}\quad
  CET6:\textbf{639}
  \item Major courses: \scriptsize Linear Algebra and Analytic Geometry(99), Calculus(96), Circuits and Electronics(99), 
  Automatic Control Principle(99), Environment Perception of Intelligent Vehicle(98), Planning and Decision-Making for Intelligent Vehicle(96), Structure of Automobile(97)
\end{itemize}



\section{\faGithub\ Experience}
\datedsubsection{\textbf{FLAG Inc.} California, America}{Feb. 2021 -- Present}
\role{Summer Intern}{Manager: xxx}
Brief introduction: xxx.
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{Tencent TAD Sim Autonomous Driving Simulation Software Development}}{Nov. 2022 -- Present}
\role{C++, Linux, Protobuf}{Team Projects, collaborated with teacher Quan Wang}
Brief introduction: xxx
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{Overall integration technology development of ground unmanned vehicles of Beijing Institute of Aerospace Launch Technology}}{Mar. 2023 -- May. 2023}
\role{C++, Shell, Linux}{Individual Projects}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faTrophy\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Silver medal, Award on 2021 Formula Student Autonomous China (delayed by Covid-19) }{Jun. 2022}
\datedline{\textit{\nth{1} Prize}, Bronze medal, Award on 2022 Formula Student Autonomous China }{Sep. 2022}
\datedline{\textit{\nth{1} Prize} Scholarship }{May. 2023}
\datedline{\textit{Other awards: } Excellent Student, \textit{\nth{2} Prize} Physics Competition for Colleges in Shandong} {2022}

\section{\faCogs\ Technical Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C++(mastered) > Python(skilled), C, Markdown, Shell, LaTex, HTML, CSS
  \item Platform: Linux
  \item Development: Web, xxx
\end{itemize}


\section{\faInfoCircle\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/255isWhite
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
